\mytitle

### 2021-12-08 paper.tex
adding references

\documentclass[10pt,DIV16,twocolumn]{scrartcl}

@@

The dilogarithm \cite{lewin} is a special function, which appears in
many physics applications, for example in the calculation of quantum
corrections in quantum field theory.  The investigation of new models
beyond the Standard Model of particle physics with a large parameter
space require the evaluation of the dilogarithm (and other functions)
billions of times.  Such investigations thus require a fast evaluation
of the dilogarithm.  In the past many time-efficient algorithms have
been proposed \cite{}, which are implemented, for example, in program
libraries for numerical physics and mathematics
\cite{root,gsl,cephes}.

@@

C, C++ and FORTRAN implementations of the presented algorithm can be
found in the Polylogarithm package \cite{polylogarithm}.

>>>>

\documentclass[10pt,DIV16,twocolumn,numbers=noenddot]{scrartcl}

@@

The dilogarithm \cite{lewin} is a special function, which appears in
many physics applications, for example in the calculation of quantum
corrections in quantum field theory.  The investigation of new models
beyond the Standard Model of particle physics with a large parameter
space require the evaluation of the dilogarithm (and other functions)
billions of times.  Such investigations thus require a fast evaluation
of the dilogarithm.  In the past many time-efficient algorithms have
been invented (see e.g.~\cite{koelbigDilog,ginsberg,morris}) and many
are implemented, for example, in general-purpose physics and
mathematics program libraries \cite{root,gsl,cephes}.

@@

C, C++ and FORTRAN implementations of the presented algorithm can be
found in the Polylogarithm library \cite{polylogarithm}.
